Stable individual differences in strategies within, but not between, visual search tasks

### 2019-05-30 Manuscript/manuscript.tex
getting ready to submit again!

%% *** Do not adjust lengths that control margins, column widths, etc. ***
\usepackage{subfigure}
% \usepackage{lineno}
% \usepackage{hyperref}
\usepackage{graphicx}
% \usepackage{natbib}

@@

Here we focus on one source of individual differences in visual search: strategy. By strategy we mean a collection of search behaviours from which all observers can freely choose. Examples include adopting a systematic left-to-right and top-to-bottom strategy \cite{gilchrist2006}, or prioritizing locations that, based on knowledge or context, are more likely to contain the target \cite{wolfe2015}. A striking example of the effect of strategy is given by \cite{boot2006}. They asked participants to monitor a cluttered display for an object changing colour or suddenly appearing. Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, which was negatively correlated with detection performance.

@@

A similar range of strategies, from random to near-optimal, has been found by \cite{irons-leber2016} with the Adaptive Choice Visual Search (ACVS) paradigm. This paradigm involves stimuli made up of small coloured boxes (red, blue, green and a fourth colour that varies from red, through purple, to blue and back again) with numerals written inside them (Figure \ref{fig:exampleStimuli}). The target is a defined as a red or blue box containing one of four numerals (e.g., 2-5), and on each trial one target of each colour is present. The participant's task is to find one of either target as quickly as possible and report the numeral. On trials in which the fourth colour is red (or close to red), participants should search through the blue boxes and report the blue target, as there will be fewer distracters. As the fourth colour changes to through purple to blue, participants should update their strategy and search for the red target. The results showed that participants varied substantially along two key dimensions: how frequently they used the more effective target colour to search (varying from chance performance to near optimal), and how often they changed between colours. Further work \cite{irons-leber2018} has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.83$ ($95\%$ CI $= [0.72, 0.90]$) for optimal choices.

@@

The methods and planned analysis for this study were registered on the Open Science Framework\endnote{https://osf.io/scv4u/} before data collection started.

@@

Each search display was composed of 54 red, blue, green and variable-coloured small squares arranged in three concentric rings around fixation (see \ref{fig:exampleStimuli}). Variable distractors changed colours from trial-to-trial according to a 24 trial cyclical pattern: these distractors would be red for five trials, then across a period of seven trials, they would gradually change colour from red to blue. The variable distractors would then be blue for five trials, and then gradually transition back to red. 
%A missing detail reviewers might want to know here is how many distractors are variable vs fixed colors

@@

We view these findings not as a discouraging result, but as thought-provoking and exciting. Vogel and Awh \cite{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to constraining potential theories of the underlying cognitive mechanisms. Our results suggest that context and structure of the task also needs to be taken into account. Understanding how an individual's behaviour varies across different search tasks can lead to the development of a comprehensive theory of search.

>>>>

%% *** Do not adjust lengths that control margins, column widths, etc. ***
\usepackage{subfigure}
% \usepackage{lineno}
% \usepackage{hyperref}
\usepackage{graphicx}

@@

Here we focus on one source of individual differences in visual search: strategy. By strategy we mean a collection of search behaviours from which all observers can freely choose. Examples include adopting a systematic left-to-right and top-to-bottom strategy \cite{gilchrist2006}, or prioritizing locations that, based on knowledge or context, are more likely to contain the target \cite{wolfe2015}. A striking example of the effect of strategy is given by Boot, Kramer, Becic, Wiegmann and Kubose \citeyear{boot2006}. They asked participants to monitor a cluttered display for an object changing colour or suddenly appearing. Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, which was negatively correlated with detection performance.

@@

A similar range of strategies, from random to near-optimal, has been found by Irons and Leber \citeyear{irons-leber2016} with the Adaptive Choice Visual Search (ACVS) paradigm. This paradigm involves stimuli made up of small coloured boxes (red, blue, green and a fourth colour that varies from red, through purple, to blue and back again) with numerals written inside them (Figure \ref{fig:exampleStimuli}). The target is a defined as a red or blue box containing one of four numerals (e.g., 2-5), and on each trial one target of each colour is present. The participant's task is to find one of either target as quickly as possible and report the numeral. On trials in which the fourth colour is red (or close to red), participants should search through the blue boxes and report the blue target, as there will be fewer distracters. As the fourth colour changes to through purple to blue, participants should update their strategy and search for the red target. The results showed that participants varied substantially along two key dimensions: how frequently they used the more effective target colour to search (varying from chance performance to near optimal), and how often they changed between colours. Further work \cite{irons-leber2018} has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.83$ ($95\%$ CI $= [0.72, 0.90]$) for optimal choices.

@@

The methods and planned analysis for this study were registered on the Open Science Framework\footnote{https://osf.io/scv4u/} before data collection started.

@@

Each search display was composed of 54 red, blue , green and variable-coloured small squares (14 of each colour) arranged in three concentric rings around fixation (see \ref{fig:exampleStimuli}). Variable distractors changed colours from trial-to-trial according to a 24 trial cyclical pattern: these distractors would be red for five trials, then across a period of seven trials, they would gradually change colour from red to blue. The variable distractors would then be blue for five trials, and then gradually transition back to red.

@@

We view these findings not as a discouraging result, but as thought-provoking and exciting. Vogel and Awh \citeyear{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to constraining potential theories of the underlying cognitive mechanisms. Our results suggest that context and structure of the task also needs to be taken into account. Understanding how an individual's behaviour varies across different search tasks can lead to the development of a comprehensive theory of search.
